\mytitle

### 2012-02-23 papers/SAS2012/implicitization.tex
Ça rentre dans 15 pages !

\renewcommand{\baselinestretch}{.97}

@@

The analysis starts by identifying the tests taken and not taken during the first iteration of the loop, starting in the loop initialization. The branches not taken are pruned from the loop body, yielding:
\begin{lstlisting}[numbers=none]
  while(1) {
    if(x <= 50) y++;
    else break; /* not taken in phase 1 */
    if(y < 0) break;
    x++;
  }
\end{lstlisting}

@@

Guided static analysis, as proposed by \cite{DBLP:conf/sas/GopanR07}, applies to the transition
graph of the program. We now present a new technique applying this analysis on the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \ref{sec:path_focusing}, except
that we call the abstract values $X_i^s$ instead of $X_i$ to leave room for
another abstract value $X_i^d$ later in the algorithm.

@@

\subsection{Algorithm}

@@

\begin{algorithm}
	\caption{Guided static analysis on implicit multigraph}
	\label{algo:combined}
	\begin{algorithmic}[1] 
	\input{algo/algo-combined.tex}
	\end{algorithmic}
\end{algorithm}

@@

Step~\ref{step:ascending} corresponds to the application of
path-focusing \cite{Monniaux_Gonnord_SAS11} to
the elements of $A$ until $A$ is empty. 
When $A$ becomes empty, it means the
invariant computation of the subgraph is finished. As proposed by
\cite{DBLP:conf/sas/GopanR07}, we can do some narrowing iterations.
These narrowing iterations allow to recover precision lost by
widening, \emph{before} computing and taking into account new feasible paths.
Thus, our technique combines both the advantages of \emph{Guided Static
Analysis} and \emph{Path-focusing}.

@@

\begin{algorithm}
	\caption{ComputeNewPaths}
	\label{algo:computepaths}
	\begin{algorithmic}[1] 
	\input{algo/compute-paths.tex}
	\end{algorithmic}
\end{algorithm}

@@

	\node[PRstate] (n00) {$p_4$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_5$};
	\node[PRstate] (n1) [below of=n0] {$p_{10}$};
	\node (label) [below of=n1, yshift=1.2cm] {Step 1};

@@

	\node[PRstate] (n00) {$p_4$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_5$};
	\node[PRstate] (n1) [below of=n0] {$p_{10}$};
	\node (label) [below of=n1, yshift=1.2cm] {Step 2};

@@

\begin{algorithm}[!h]
\caption{Disjunctive invariant computation with implicit paths}\label{gulwani2}
\label{algo:disjunctive}
\begin{algorithmic}[1] 
\WHILE {true}
	\STATE $res \gets SmtSolve\left[g(p_i)\right]$
	\IF {$res = unsat$}
		\STATE \textbf{break}
	\ENDIF
	\STATE Compute the path $\tau_{i,k}$ from $res$ 
	\STATE Take $j \in \{ l | d_l = true\}$ 
	\STATE Update($X_{i,\sigma_i(j,k)})$
\ENDWHILE
\end{algorithmic}
\end{algorithm}

>>>>

\renewcommand{\baselinestretch}{1}

@@

The analysis starts by identifying the tests taken and not taken during the first iteration of the loop, starting in the loop initialization. The branches not taken are pruned from the loop body, yielding:
\vspace{-.5em}
\begin{lstlisting}[numbers=none]
  while(1) {
    if(x <= 50) y++;
    else break; /* not taken in phase 1 */
    if(y < 0) break;
    x++;
  }
\end{lstlisting}
\vspace{-.5em}

@@

Guided static analysis, as proposed by \cite{DBLP:conf/sas/GopanR07}, applies to the transition
graph of the program. We now present a new technique applying this analysis on the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \ref{sec:path_focusing}, except
that we call the abstract values $X_i^s$ instead of $X_i$ to leave room for
another abstract value $X_i^d$ later.

@@

The ascending iteration applies path-focusing
\cite{Monniaux_Gonnord_SAS11} to a subset of the multigraph. As
\cite{DBLP:conf/sas/GopanR07}, we do some narrowing, to recover
precision lost by widening, \emph{before}
computing and taking into account new feasible paths. Thus, our
technique combines the advantages of \emph{Guided Static
  Analysis} and \emph{Path-focusing}.

% MM: ce titre bouffe pas mal de place pour une valeur ajoutée faible
%\subsection{Algorithm}

@@

\vspace{-1em}
\begin{algorithm}
	\caption{Guided static analysis on implicit multigraph}
	\label{algo:combined}
	\begin{algorithmic}[1] 
	\input{algo/algo-combined.tex}
	\end{algorithmic}
\end{algorithm}
\vspace{-1em}

@@

@@

\vspace{-1em}
\begin{algorithm}
	\caption{ComputeNewPaths}
	\label{algo:computepaths}
	\begin{algorithmic}[1] 
	\input{algo/compute-paths.tex}
	\end{algorithmic}
\end{algorithm}
\vspace{-1em}

@@

	\node[PRstate] (n00) {$p_4$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_5$};
	\node[PRstate] (n1) [below of=n0] {$p_{10}$};
	\node (label) [left of=n00, node distance=1cm] {\bf Step 1};

@@

	\node[PRstate] (n00) {$p_4$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_5$};
	\node[PRstate] (n1) [below of=n0] {$p_{10}$};
	\node (label) [left of=n00, node distance=1cm] {\bf Step 2};

@@

\vspace{-1em}
\begin{algorithm}[!h]
\caption{Disjunctive invariant computation with implicit paths}\label{gulwani2}
\label{algo:disjunctive}
\begin{algorithmic}[1] 
\WHILE {true}
	\STATE $res \gets SmtSolve\left[g(p_i)\right]$
	\IF {$res = unsat$}
		\STATE \textbf{break}
	\ENDIF
	\STATE Compute the path $\tau_{i,k}$ from $res$ 
	\STATE Take $j \in \{ l | d_l = true\}$ 
	\STATE Update($X_{i,\sigma_i(j,k)})$
\ENDWHILE
\end{algorithmic}
\end{algorithm}
\vspace{-1em}
